---
title: "R Notebook"
output: html_notebook
---

Orange
```{r}
data(Orange)
# Orange
# plot(Orange)
# typeof(Orange)
plot(age~circumference, data=Orange)
# plot(Orange$circumference, Orange$age)
lm_result = lm(age~circumference, data=Orange)
typeof(lm_result)

?abline

abline(lm(age~circumference, data=Orange), col='blue')
lines(loess.smooth(Orange$circumference, Orange$age), col='red')
```

Demo
```{r}
demo(graphics)
```

ggplot2 install
```{r}
install.packages('ggplot2')
library(ggplot2)
```

ggplot2
```{r}
# Reading data
data(Orange)
Orange$circumference

qplot(circumference , age, data=Orange)
abline(lm(age~circumference, data=Orange), col='blue')
lines(loess.smooth(Orange$circumference, Orange$age), col='red')
```

qplot with filtering
```{r}
qplot(circumference, age, data=Orange[Orange$Tree==1,], geom='line')
qplot(circumference, age, data=Orange[Orange$Tree==1,], geom=c('line', 'point'))
```

Boxplot
```{r}
boxplot(circumference~Tree, data=Orange)
qplot(Tree, circumference, data=Orange, geom='boxplot')
```

Boxplot with individual observations
```{r}
boxplot(circumference~Tree, data=Orange)
points(circumference~Tree, data=Orange)
qplot(Tree, circumference, data=Orange, geom=c('boxplot', 'point'))
```

Histogram of the orange dataset
```{r}
hist(Orange$circumference)
qplot(circumference, data=Orange, geom='histogram')
```

Histogram with the reference line at the median value in red
```{r}
hist(Orange$circumference)
abline(v=median(Orange$circumference), col='red')

#ggplot
qplot(circumference, data=Orange, geom='histogram') + geom_vline(xintercept = median(Orange$circumference), colour='red')
```

Lattice and Trellis plots
```{r}
require(lattice)
myPanel <- function(x, y) {
  panel.xyplot(x, y);
  panel.lmline(x, y, col='blue')
  panel.loess(x, y, col='red')
}
xyplot(age~circumference, data=Orange, panel=myPanel)
```

```{r}
myPanel <- function(x, y) {
  panel.xyplot(x, y, type='b') # the observations
}
xyplot(age~circumference | Tree, data=Orange, panel=myPanel);
```

## Scatterplots with individual observations
```{r}
xyplot(age~circumference, data=Orange)
```
```{r}
qplot(circumference, age, data=Orange)
```

## Scatterplots of the orange dataset with faceting
```{r}
xyplot(age~circumference | Tree, data=Orange)
```
```{r}
qplot(circumference, age, data=Orange, facets=~Tree)
```

## Faceting scatterplots with line and points
```{r}
xyplot(age~circumference | Tree, data=Orange, type='b')
```
```{r}
qplot(circumference, age, data=Orange, geom=c('line', 'point'), facets=~Tree)
```

## Scatterplots with grouping data
```{r}
xyplot(age~circumference, data=Orange, groups=Tree, type='b')
```
```{r}
qplot(circumference, age, data=Orange, color=Tree, geom=c('line', 'point'))
```

## Boxplots of the orange dataset
```{r}
bwplot(circumference~Tree, data=Orange)
```
```{r}
qplot(Tree, circumference, data=Orange, geom='boxplot')
```

## Histograms of the orange dataset
```{r}
histogram(Orange$circumference, type='count')
```
```{r}
qplot(circumference, data=Orange, geom='histogram')
```

## Histograms with the reference line at the median value in red
```{r}
histogram(~circumference, data=Orange, type='count', panel=function(x, ...){
  panel.histogram(x, ...);
  panel.abline(v=median(x), col='red')
})
```
```{r}
qplot(circumference, data=Orange, geom='histogram') + 
  geom_vline(xintercept = median(Orange$circumference), colour='red')
```

## ggplot2 and the grammar of graphics

```{r}
require(ggplot2)
data(Orange)

ggplot(data=Orange, aes(x=circumference, y=age, color=Tree)) +
  geom_point() +
  stat_smooth(method='lm', se=FALSE)
```

```{r}
qplot(circumference, age, data=Orange, color=Tree, geom=c('point', 'smooth'), method='lm', se=FALSE)
```

