---
title: "ggplot2 cookbook"
output: html_notebook
---

# Getting Started

## Histograms and density attributes (1 value, 1 grouping)
```{r}
## head(iris)
qplot(iris$Petal.Length, geom='histogram', color=iris$Species, fill=iris$Species, alpha=I(0.5))
qplot(iris$Petal.Length, geom='density', color=iris$Species, fill=iris$Species, alpha=I(0.5))
```

## Bar charts (factor/count, grouping)
```{r}
# install.packages("ggplot2movies")
require(ggplot2)
require(ggplot2movies)
# data(package='ggplot2')
# data(package='ggplot2movies')
# data(movies)
# head(movies)The Garden of Words.2013.1080p.BDRip.x265.AC3-HDione.mkvThe Garden of Words.2013.1080p.BDRip.x265.AC3-HDione.mkv
# nrow(movies)

# https://stat.ethz.ch/pipermail/r-help/2011-March/272790.html
test <- 'Action'
head(movies[test])
head(movies[[test]])

budgetByType <- function(type) {
  ret <- data.frame(movies[movies[[type]]==1, c('budget', 'Short', 'year')])
  ret$Type = type
  return(ret)
}

budgetByType('Action')

d1 <- data.frame(movies[movies$Action==1, c('budget', 'Short', 'year')])
d1$Type = 'Action'
d2 <- data.frame(movies[movies$Animation==1, c('budget', 'Short', 'year')])
d2$Type = 'Animation'
nrow(d1)
nrow(d2)

d3 <- budgetByType('Comedy')
d4 <- budgetByType('Drama')
d5 <- budgetByType('Documentary')
d6 <- budgetByType('Romance')

myMovieData <- rbind(d1, d2, d3, d4, d5, d6)

typeof(myMovieData$Type)
class(myMovieData$Type)
qplot(Type, data=myMovieData, geom='bar', fill=Type)

```

```{r}
qplot(Type, data=myMovieData, geom='bar', fill=factor(year))
class(factor(myMovieData$Short))
class(myMovieData$Short)
class(myMovieData$Type)
qplot(Type, data=myMovieData, geom='bar', fill=factor(Short))
```
As you probably noticed in this last example, we assigned the Short variable to the
fill argument, but in the assignment, we also converted the variable to factor,
while in the previous example, when we used the Type variable, we did not do
so. The reason is that the fill aesthetic attribute, in this case, needed a discrete
variable, which defined different levels. These, in turn, were assigned to different
colors. The Type variable of the previous example was already a factor, where each
level represented the movie type. On the other hand, the Short variable is actually
numeric: 0 for regular movies and 1 for short movies. For this reason, we had to
convert it first to a factor, so qplot could identify this variable as indicating two
levels of a discrete variable.

```{r}
qplot(Type, data=myMovieData, geom='bar', fill=factor(Short), position='stack')
ggplot(data=myMovieData, aes(x=Type, colour=Type, fill=factor(Short))) +
  geom_bar(position='dodge')
```

```{r}
qplot(Type, data=myMovieData, fill=factor(Short), postion='dodge')
ggplot(data=myMovieData, aes(x=Type, fill=factor(Short))) +
  geom_bar(position='dodge')
```

```{r}
qplot(Type, data=myMovieData, fill=factor(Short), position='fill')
ggplot(data=myMovieData, aes(x=Type, fill=factor(Short))) +
  geom_bar(position = 'fill')
```

## Boxplots (value/factor)
```{r}
qplot(Type, budget, data=myMovieData, geom='boxplot')

# plot with NA removed
qplot(Type, budget, data=myMovieData[!is.na(myMovieData$budget),], geom='boxplot')

```

```{r}
ggplot(data=myMovieData, aes(x=Type, y=budget, fill=Type)) + geom_boxplot()
```

Budget with log
```{r}
ggplot(data=myMovieData, aes(x=Type, y=log(budget), fill=Type)) + geom_boxplot()
```

```{r}
qplot(Type, budget, data=myMovieData, geom=c('boxplot', 'point'), log='y')
```

```{r}
qplot(Type, budget, data=myMovieData, geom=c('jitter', 'boxplot'), alpha=I(0.6), log='y')
```

## Scatterplots (value/value, value/factor, grouping)
```{r}
qplot(dose, len, data=ToothGrowth, geom='point')
## Alternative coding
qplot(dose, len, data=ToothGrowth, col=supp)
```
```{r}
qplot(dose, len, data=ToothGrowth, geom='point', facets=.~supp)
```

Show tendency
```{r}
qplot(dose, len, data=ToothGrowth, geom=c('point', 'smooth'), facets = .~supp)
```

## Time series (value/date)
```{r}
head(economics)
```
```{r}
#install.packages('plotly')
library(plotly)
p <- qplot(date, unemploy, data=economics, geom='line')
ggplotly(p)

```

## Buggle charts and dot plots (factor/date~value)
```{r}
qplot(year, Type, data=myMovieData, size=budget)
```

